%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume2} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Shivam Prasad} % Your name
\address{(+91)~$\cdot$~81467-89755   \\   2017csb1108@iitrpr.ac.in} % Your phone number and email
\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Indian Institute of Technology, Ropar} \hfill {\em July 2017 - Present} \\ 
B.Tech in Computer Science \& Engineering \\
Current GPA: 8.66/10

{\bf CISCE}\\ 
ISC(Class 12): 95\% \hspace{4.6cm} ICSE(Class 10): 96.8\%
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Technical Strengths}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Computer Languages & C/C++, Java \\
    Tools/OS & Android Studio, MATLAB, OpenCV, Git, Linux
    \end{tabular}
    
    \end{rSection}
\begin{rSection}{Projects}

\begin{rSubsection}{Ported Code for Robust Heart Rate Measurement from MATLAB to Android App}{}{Android Studio, Java, OpenCV, Matlab}{May 2018 - July 2018}
\item Ported Dr. Antony Lam's and Dr.Yoshinori Kuno's MATLAB code for \textit{Robust Heart Rate Measurement from Video Using Select Random Patches} to Android.
\item Used OpenCV for face detection using pretrained HAAR Cascade Classifiers and image data processing.
\item Wrote Java code for some MATLAB functions and OpenCV image data processing from scratch.
\item Implemented matrix operations in Java using Apache Commons Math library.
\item Project was supervised by Dr. Abhinav Dhall.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{K Means for Character Array in C}{}{}{}
\item Wrote a program from scratch for applying K-Means Clustering Algorithm and Logistic Regression on Character-Array in C.
\item Used for filtering spam messages from non-spam messages. 
\item Trained and Tested on a subset of NUS SMS Corpus.
\end{rSubsection}

\begin{rSubsection}{Other Projects}{}{}{}
\item Implemented Quine-McCluskey algorithm for logic minimization in C++.
\item Made a polar to rectangular coordinate converter for Basys 3 in verilog.
\item Automated Service Robot using Raspberry Pi. (Ongoing Project)
\end{rSubsection}

%------------------------------------------------

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Relevant Courses}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        Computer Science & Introduction to Programming in C, Data Structures, Digital Logic Design \\
        Mathematics & Calculus, Linear Algebra, Discrete Mathematics, Differential Equations\\
        Others & Signals and Systems    
    \end{tabular}
    
\end{rSection}

\begin{rSection}{Positions of Responsibility}

    \begin{rSubsection}{Coding Club Coordinator}{August 2018 - Present}{}{}
        \item Conduct regular coding sessions for juniors and organise regular coding contests.
    \end{rSubsection}

    \begin{rSubsection}{Quizzing Club Representative}{August 2018 - Present}{}{}
        \item Organise club sessions and participate in quizzing events. 
    \end{rSubsection}

\end{rSection}

\begin{rSection}{Miscellaneous}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        JEE Rank & Secured rank 1882 (Out of 1.5 million candidates) in Joint Entrance Exam, 2017. \\
        Volunteer Work & Worked as a part of event management team in college fests.\\
        & Volunteered for Baja Sae India.
    \end{tabular}
\end{rSection}
%----------------------------------------------------------------------------------------

\end{document}
